Longer Term All-Cause and Cardiovascular Mortality With Intensive Blood Pressure Control

### 2024-07-28 README.Rmd
adjust legend

# specification for tables
rspec <- round_spec() |>
  round_using_magnitude(digits = c(2, 1, 0),
                        breaks = c(10, 100, Inf))

@@

tar_load(names = c(recoders,
                   base_viz_inc,
                   base_viz_eff,
                   long_viz,
                   bp_viz,
                   tbl_characteristics,
                   base_ds, 
                   long_ds,
                   long_inf,
                   base_inf,
                   ndi_baseline))

@@

inline$base_ds <- base_ds |>
  mutate(across(matches("est$|lwr$|upr"), table_value),
         across(matches("^n_"), ~table_value(as.integer(.x)))) |>
  as_inline(tbl_variables = tbl_variables,
            tbl_values = setdiff(names(base_ds), tbl_variables))

@@

inline$long_inf <- long_inf |>
  mutate(across(matches("est$|lwr$|upr"), table_value),
         across(matches("^n_"), ~table_value(as.integer(.x)))) |>
  as_inline(tbl_variables = tbl_variables,
            tbl_values = setdiff(names(long_inf), tbl_variables))

@@

bp_viz_5yr <- bp_viz |> 
  getElement('levels') |> 
  getElement('data') |> 
  filter(source == 'EHR', 
         time_months == 60)

@@

bp_viz_10yr <- bp_viz |> 
  getElement('levels') |> 
  getElement('data') |> 
  filter(source=='EHR',
         time_months == 120)

@@

bp_diff_5yr <- bp_viz |> 
  getElement('diff') |> 
  getElement('data') |> 
  filter(time_months == 60)

t_atten_sbp <- bp_viz |> 
  getElement('diff') |> 
  getElement('data') |> 
  filter(source == 'EHR',
         find_signchange_lgl(Lower)) |> 
  pull(time_months) |> 
  divide_by(12)

>>>>

# specification for tables
rspec <- round_spec() %>%
  round_using_magnitude(digits = c(2, 1, 0),
                        breaks = c(10, 100, Inf))

@@

withr::with_dir(
  here::here(),
  code = {
    tar_load(names = c(recoders,
                       base_viz_inc,
                       base_viz_eff,
                       long_viz,
                       bp_viz,
                       tbl_characteristics,
                       base_ds, 
                       long_ds,
                       long_inf,
                       base_inf,
                       ndi_baseline))
  }
)

```{r make-results, include=FALSE}

@@

inline$base_ds <- base_ds %>%
  mutate(across(matches("est$|lwr$|upr"), table_value),
         across(matches("^n_"), ~table_value(as.integer(.x))))

inline$base_ds <- as_inline(inline$base_ds,
                            tbl_variables = tbl_variables,
                            tbl_values = setdiff(names(base_ds), 
                                                 tbl_variables))

@@

inline$long_inf <- long_inf %>%
  mutate(across(matches("est$|lwr$|upr"), table_value),
         across(matches("^n_"), ~table_value(as.integer(.x))))

inline$long_inf <- as_inline(inline$long_inf,
                             tbl_variables = tbl_variables,
                             tbl_values = setdiff(names(long_inf),
                                                  tbl_variables))

@@

bp_viz_5yr <- bp_viz %>% 
  getElement('levels') %>% 
  getElement('data') %>% 
  filter(source == 'EHR', 
         time_months == 60)

@@

bp_viz_10yr <- bp_viz %>% 
  getElement('levels') %>% 
  getElement('data') %>% 
  filter(source=='EHR',
         time_months == 120)

@@

bp_diff_5yr <- bp_viz %>% 
  getElement('diff') %>% 
  getElement('data') %>% 
  filter(time_months == 60)

t_atten_sbp <- bp_viz %>% 
  getElement('diff') %>% 
  getElement('data') %>% 
  filter(source == 'EHR',
         find_signchange_lgl(Lower)) %>% 
  pull(time_months) %>% 
  divide_by(12)

### 2024-07-28 index.qmd
adjust legend

---
title: "Longer Term All-Cause and Cardiovascular Mortality With Intensive Blood Pressure Control"
subtitle: "A Secondary Analysis of a Randomized Clinical Trial"
author: "Byron C. Jaeger, PhD"
institute: "Wake Forest University School of Medicine"
format: 
  revealjs:
    slide-number: true
    footer: Slides available at https://www.byronjaeger.com/talk/ (google byron jaeger biostats talks)
    width: 1280
    height: 720
    fig-dpi: 300
    fig-width: 8
    fig-height: 6
    fig-align: "center"
    message: false
    bibliography: doc/refs.bib
    reference-location: document
knitr:
  opts_chunk:
    out.width: "100%"
---

@@

@@

base_viz_inc$inc_acm[[1]]$plot + 
  annotate(geom = 'rect',
           xmin = 9.8,
           ymin = .18,
           xmax = Inf,
           ymax = .35,
           fill = 'black',
           alpha = 1) + 
  theme_fig(legend.position = 'inside',
            legend.position.inside = c(0.75, 0.20))

@@

base_viz_inc$inc_acm[[1]]$plot + 
  theme_fig(legend.position = 'inside',
            legend.position.inside = c(0.75, 0.20))

@@

base_viz_inc$inc_cvd[[1]] + 
  annotate(geom = 'rect',
           xmin = 9.8,
           ymin = .02,
           xmax = 13.2,
           ymax = .25,
           fill = 'black',
           alpha = 1) + 
  theme_fig(legend.position = 'inside',
            legend.position.inside = c(0.5, 0.69))

@@

base_viz_inc$inc_cvd[[1]] +
  theme_fig(legend.position = 'inside',
            legend.position.inside = c(0.5, 0.69))

>>>>

---
title: "Longer Term All-Cause and Cardiovascular Mortality With Intensive Blood Pressure Control"
subtitle: "A Secondary Analysis of a Randomized Clinical Trial"
author: "Byron C. Jaeger, PhD"
institute: "Wake Forest University School of Medicine"
format: 
  revealjs:
    slide-number: true
    width: 1280
    height: 720
    fig-dpi: 300
    fig-width: 8
    fig-height: 6
    fig-align: "center"
    message: false
    bibliography: doc/refs.bib
    reference-location: document
knitr:
  opts_chunk:
    out.width: "100%"
---

@@

- Slides are available at https://www.byronjaeger.com/talk/ (google byron jaeger biostats talks)

@@

base_viz_inc$inc_acm[[1]]$plot + 
  annotate(geom = 'rect',
           xmin = 9.8,
           ymin = .18,
           xmax = Inf,
           ymax = .35,
           fill = 'black',
           alpha = 1) + 
  theme_fig(legend.position = 'top')

@@

base_viz_inc$inc_acm[[1]]$plot + 
  theme_fig(legend.position = 'top')

@@

base_viz_inc$inc_cvd[[1]] + 
  annotate(geom = 'rect',
           xmin = 9.8,
           ymin = .02,
           xmax = 13.2,
           ymax = .25,
           fill = 'black',
           alpha = 1) + 
  theme_fig(legend.position = 'top')

@@

base_viz_inc$inc_cvd[[1]] +
  theme_fig(legend.position = 'top')
